Machine Learning for NFT Price Predictions

### 2023-11-15 paper/main.tex
preliminary results

% useful packages
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{csquotes}
\usepackage{caption,subcaption}
\captionsetup{compatibility=false}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{float}
\def\UrlFont{\rmfamily}

@@

\subsection{Exploratory analysis}
% TODO: summary stats with sample size
\begin{figure}[H]
    \includegraphics[width=\textwidth]{../figures/price_date.png}
    \caption{Trade Price by Date}
\end{figure}

@@

\section{Methodology}
\label{sec: method}
For benchmarking, I will use an OLS model. For the main model, I will use a neural network with a fully connected layer. I will also explore other deep learning methods, including convolutional neural networks (CNNs) and recurrent neural networks (RNNs). This is currently work in progress.

\section{Results}
\label{sec: results}

\section{Conclusion}
\label{sec: conclusion}

@@

\newpage
\printbibliography

>>>>

% useful packages
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{csquotes}
\usepackage{caption,subcaption}
\captionsetup{compatibility=false}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{float}
\usepackage{multirow}
\def\UrlFont{\rmfamily}

@@

\subsection{Features and target variables}
Here I outline the features and target variables used in this project. The target variable is the price of the NFT. The features are divided into four categories: market, base traits, extra traits, and last trade. The features are summarized in Table \ref{tab:feature_columns}.
\begin{table}[H]
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Feature Category} & \textbf{Feature} & \textbf{Description} \\ \hline

    \multirow{4}{*}{Market} & volume\_eth & daily market volume (ETH) \\ \cline{2-3} 
    & price\_p5\_eth & daily 5-percentile price (ETH) \\ \cline{2-3} 
    & price\_max\_eth & daily highest price (ETH) \\ \cline{2-3} 
    & price\_min\_eth & daily minimum (floor) price (ETH)\\ \hline

    \multirow{5}{*}{Base Traits} & rarity\_rank & rarity rank measured by OpenRarity \\ \cline{2-3} 
    & Background\_count & number of items with the same \textit{Background} trait \\ \cline{2-3} 
    & Mouth\_count & number of items with the same \textit{Mouth} trait \\ \cline{2-3} 
    & Eyes\_count & number of items with the same \textit{Eyes} trait\\ \cline{2-3} 
    & Fur\_count & number of items with the same \textit{Fur} trait \\ \hline

    \multirow{3}{*}{Extra Traits} & Hat\_count & number of items with the same \textit{Hat} trait \\ \cline{2-3} 
    & Clothes & number of items with the same \textit{Clothes} trait \\ \cline{2-3} 
    & Earring\_count & number of items with the same \textit{Earring} trait \\ \hline

    \multirow{2}{*}{Last Trade} & last\_trade\_timediff & time since the last time this item was traded \\ \cline{2-3} 
    & last\_trade\_price & price at the last time this item was traded\\ \hline
    \end{tabular}
    \caption{Feature Columns Description (Bored Ape Yacht Club)}
    \label{tab:feature_columns}
\end{table}

\subsection{Exploratory analysis}
% TODO: summary stats with sample size
%\subsubsection{Summary statistics}

\subsubsection{Price history}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{../figures/price_date.png}
    \caption{Trade Price by Date}
\end{figure}

@@

\subsubsection{Principal component analysis}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{../figures/pca_1.png}
    \caption{PCA(3) plot of NFT prices (Bored Ape Yacht Club)}
\end{figure}

\section{Methodology}
\label{sec: method}
For benchmarking, I will use an OLS model. For the main model, I will use a neural network with a fully connected layer. I will also explore other deep learning methods, including convolutional neural networks (CNNs) and recurrent neural networks (RNNs). I choose Mean Squared Error (MSE) as the objective function to minimize. This is currently work in progress.

\section{Results}
\label{sec: results}
I present my preliminary results.
\subsection{Benchmarking}
MSE metric for benckmark models:
\begin{table}[H]
    \centering
\begin{tabular}{|p{8em}|p{8em}|}
    \hline
    \textbf{Model} & \textbf{MSE} \\ \hline
    OLS & 455.8 \\ \hline
    Random Forest & 220.1 \\ \hline
\end{tabular}
\end{table}

%\section{Conclusion}
%\label{sec: conclusion}

@@

\newpage
\nocite{*}
\printbibliography
